SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-22 scipy-1.0/paper.tex
Move project scope section I'm not sure if it belongs in Architecture and implementation choices, but it makes more sense there than where it was.

\subsection*{SciPy Today}
At the time of writing, the SciPy library consists of nearly 
600,000 lines of code organized in 16 subpackages. 
Over 85,000 GitHub repositories and almost 5000 packages depend
on SciPy. SciPy's GitHub repository attracts approximately 20,000 unique 
visitors every two weeks, and more than 100 people contribute to a 
new release every six months. Some of the major
feature highlights from the three years preceding
SciPy 1.0 are discussed in Section \ref{sec:technical_improvements}, 
and milestones in its history are highlighted in Figure~\ref{fig:timeline}.

\begin{figure}[H]
\centering
\includegraphics[width=0.7\textwidth]{static/scipy_timeline}
\caption{Major milestones from SciPy's initial release in 2001 to
the release of SciPy 1.0 in 2017. Logos reprinted with permission.}
\label{fig:timeline}
\end{figure}

@@

\section*{Key technical improvements}
\label{sec:technical_improvements}
Here we describe key technical improvements made in the last three years.

>>>>

\subsection*{Current status}

At the time of writing, SciPy produces a new release
approximately every six months, and some of the major
feature highlights from the three years preceding
SciPy 1.0 are discussed in a technical improvements
section below. Some longer-term milestone events are
highlighted in Figure~\ref{fig:timeline}.

\begin{figure}[H]
\begin{verbatim}
    2001: first SciPy release
    2005: transition to NumPy
    2007: creation of scikits
    2008: spatial module and first Cython code added
    2010: move to a 6-monthly release cycle
    2011: development moves to GitHub
    2011: Python 3 support
    2012: add a sparse graph module and unified optimization interface
    2012: removal of maxentropy
    2013: continuous integration with TravisCI
    2015: adding Cython interface for BLAS/LAPACK and a benchmark suite
    2017: add a unified C API with LowLevelCallable; remove weave
    2017: SciPy 1.0 release
\end{verbatim}
\caption{Timeline}
\label{fig:timeline}
\end{figure}

@@

\section*{Key technical improvements}

Here we describe key technical improvements made in the last three years.
